Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Explain why spearman's was adopted
@eco-ben to check and adjust.

Given the uncertainties present, the proportion of reefs that display capacity to maintain
coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
bounds respectively. Spearman's correlation coefficient was adopted to assessed the
relationship between connectivity strength and the number of years above $\beta_{0}$.
The process was then repeated with median reef depth.

>>>>

Given the uncertainties present, the proportion of reefs that display capacity to maintain
coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
bounds respectively.

The relationship between the number of years above $\beta_{0}$ and median reef depth was
then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
adopted as reef depth distributions are expected to be non-normal and highly skewed.
Furthermore, reefs are naturally of different types and experience different conditions,
and so the monotonic trends (whether the relationship consistently increase or decrease)
rather than the exact quantative relationship is of interest.
